Racial and Ethnic Differences in ETI: Outcomes

### 2024-07-07 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
cache

```{r results='asis'}
#| warning: false
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o, smooth = "loess"))
  print(loess_plot(outcome = o, facet = T, smooth = "loess"))
}))
```

@@

```{r results='asis'}
#| warning: false
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o, smooth = "bs"))
  print(loess_plot(outcome = o, facet = T, smooth = "bs"))
}))
```

@@

```{r results='asis'}
#| warning: false
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o, smooth = "bs", df = 3))
  print(loess_plot(outcome = o, facet = T, smooth = "bs", df = 3))
}))
```

@@

```{r results='asis'}
#| warning: false
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o, smooth = "gam"))
  print(loess_plot(outcome = o, facet = T, smooth = "gam"))
}))
```

@@

```{r}
invisible(lapply(continuous_outcomes), function(o) {
  f <- as.formula(paste0(
    o,
    "~ age_group + Insurance + bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
  ))
  m <- lmer(f, data = encounter)
  predict_response(model = m, terms = c("Days[all]", "Race")) %>% plot()
})
```

>>>>

```{r results='asis'}
#| warning: false
#| cache: true
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o, smooth = "loess"))
  print(loess_plot(outcome = o, facet = T, smooth = "loess"))
}))
```

@@

```{r results='asis'}
#| warning: false
#| cache: true
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o, smooth = "bs"))
  print(loess_plot(outcome = o, facet = T, smooth = "bs"))
}))
```

@@

```{r results='asis'}
#| warning: false
#| cache: true
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o, smooth = "bs", df = 3))
  print(loess_plot(outcome = o, facet = T, smooth = "bs", df = 3))
}))
```

@@

```{r results='asis'}
#| warning: false
#| cache: true
invisible(lapply(continuous_outcomes, function(o) {
  cat("\n")
  cat("\n")
  cat("##", o)
  cat("\n")
  cat("\n")
  print(loess_plot(outcome = o, smooth = "gam"))
  print(loess_plot(outcome = o, facet = T, smooth = "gam"))
}))
```

@@

## With Asian subgroup

```{r}
invisible(lapply(continuous_outcomes, function(o) {
  f <- as.formula(paste0(
    o,
    "~ age_group + Insurance + bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
  ))
  m <- lmer(f, data = encounter)
  predict_response(model = m, terms = c("Days[all]", "Race")) %>%
    plot() %>%
    print()
}))
```

## Without Asian subgroup (for clearer plotting)

```{r}
invisible(lapply(continuous_outcomes, function(o) {
  f <- as.formula(paste0(
    o,
    "~ age_group + Insurance + bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
  ))
  m <- lmer(f, data = encounter %>% filter(Race != "Asian"))
  predict_response(model = m, terms = c("Days[all]", "Race")) %>%
    plot() %>%
    print()
}))
```
